CTest Integration of Sikuli Automated GUI Testing

### 2011-06-09 Documentation/Article.tex
temp
integration with CTest

% ------------------------------------------------------------------------
\section{Integration with CTest}
% I'll write it this part
One of Sikuli's primary uses is the automation of GUI testing for software
developers.  For GUI testing, it is useful to compartmentalize different software functions and test each unit
individually.  The newest versions of Sikuli come equipped with a Unit Testing feature 
Unit Testing.  Unit Testing can be called using the IDE or by command
line and enables the user to write multiple functions in a script which are
run individually.  At the end of the run, the Sikuli output will tell the user
how many tests ran successfully and which ones failed and where.  To connect this
Unit Testing feature directly to our software, we integrated Sikuli with CTest.
.....
.....

>>>>

% ------------------------------------------------------------------------
\section{Integration with CTest}

% I'll write it this part
One of Sikuli's primary uses is the automation of GUI testing for software
developers. For GUI testing, it is useful to compartmentalize different software
functions and test each unit individually.\\

The newest versions of Sikuli come equipped with a Unit Testing feature based
on JUnit~\cite{}. Unit Testing can be called using the IDE or by command
line and enables the user to write multiple functions in a script which are
run individually. At the end of the run, the Sikuli output will tell the user
how many tests ran successfully and which ones failed and where.\\

Here we connect this Unit Testing feature to CTest, this allows us to report
results on public dashboard using CDash.
